---
title: "datatable_101"
author: "Juan Ignacio Garicoche"
date: '2022-08-18'
output: html_document
---

```{r}
library(data.table)
```


2. How to create a data.table from lists (vectors) ?

```{r}
list_1 <- c("a","b","c","d")
list_2 <- c("1","2","3","4")
list_3 <- c("aa","bb","cc","dd")

dt <- data.table::data.table(list_1, list_2, list_3)

rm(list_1, list_2, list_3, dt)
```

3. How to import csv data files as data.table ?

```{r}
dt <- fread('C:/Users/jgaricoche/Downloads/prueba_lecutra.csv')
```

4. How to import only ‘n’ rows from a csv file to create a data.table?

```{r}
dt <- fread('C:/Users/jgaricoche/Downloads/prueba_lecutra.csv', nrows=1)
```

5. How to import only specified columns from a csv file?

```{r}
dt <- fread('C:/Users/jgaricoche/Downloads/prueba_lecutra.csv', select=('fondo_fijo'))
```

6. How to get the nrows, ncolumns, datatype, summary stats of each column in a data.table

```{r}
dt <- fread('C:/Users/jgaricoche/Desktop/Facultad/DMEyF_2022/repo/datasets/bostonHousing.csv')

nrows <- nrow(dt)
ncols <- ncol(dt)
print(sapply(dt,class), end='\n')
print(summary(dt))
```

7. How to extract the row and column number of a particular cell with given criterion?

```{r}
# Get rows with highest age
subset <- dt[age == max(age, na.rm = TRUE)][,c('age','crim')]
```

10. How to check for missing values in a data.table?

```{r}
missing_values <- dt[!complete.cases(dt), ]
```

22. How to calculate count of each unique value in a given column?


22_bis. How to group by one column?

```{r}
groupby <- dt[, list(suma_grupo = sum(crim), cant_filas = .(.N), records = .N), by=rad]
```
